### 2019-05-23 thesis-template/msc-thesis.tex
update

Ellipse Equation:
\begin{align}
	r(\theta) = \frac{ab}{\sqrt{a^{2}\sin^{2}(\theta-\varphi)+b^{2}\cos^{2}(\theta-\varphi)}} =\frac{\lambda_1\lambda_2}{\sqrt{\lambda_1^2\sin^2(\theta-\varphi)+\lambda_2^2\cos^2(\theta-varphi)}}
\end{align}
That is, the singular values form the half-axes of the PCA ellipsoid, which yields us a symbolic definition for our transmission (transfer) function as weighting profiles. We compute the offset angle $\varphi$ by exploiting the atan2-function with 4-quadrant evaluation for the first singular vector. As a preliminary prep, this profile is precomputed (sampled) for all discrete angular steps for each cell (e.g. $360$). The weighting scheme which we apply is depicted in Fig. \ref{weighting}.
\begin{figure}[h]
  \centering
  {
    \includegraphics[width=0.6\textwidth]
    {img/weighting.png}
  }
  \caption{red: Intensity Profile, cyan: Transmission Profile (Glyph Ellipsoid Eq.)}
  \label{weighting}
\end{figure}
We interpret the polar functions as discrete, sampled 1D vectors with a constant angular resolution. That means, we use element-wise multiplication for the 1D-vectors in red (Intensity Profile) and cyan (Transmission Profile) to obtain a windowed version of the intensity profile and perform the following integration step to accumulate the total radiant power (flux) as follows. Note that we model angular dependent radiant intensity $\mathbf{I}(\omega) [\frac{W}{\mathop{rad}}]$ as an underlying physical entity, which is well suited for describing point light sources:

\begin{align}
	\Phi_t = \int_0^{2\pi}\mathbf{I}(\omega)\mathbf{T}(w)\mathop{d\omega}
\end{align}

Now each tensor ellipse equation has a mean transmission rate $[\%]$, which turns out to be a measure or synonym for the total transmitted rate of the incoming intensity $\mathbf{I}(\omega)$. Since there can no energy be generated from transmission profiles (only transmitting, not generating), we have to normalize every tensor ellipse equation with the highest mean transmission rate in the field. This restricts the tensor ellipse mean to a maximum of 1.0 for the one with the highest tensor magnitude. Another problem that occurs with the weighting functions is that they can yield values above 1, which would potentially generate intensity out of nothing which leads to crucially unstable behaviour. Well, but only in case energy conservation principles were not respected. However, a proper normalization can give corrective remedy
\section{Global Illumination Gradient}
\label{sec:ftle}
Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. 
Usw.

>>>>

Ellipse Equation:
\begin{align}
	r(\omega) = \frac{ab}{\sqrt{a^{2}\sin^{2}(\omega-\varphi)+b^{2}\cos^{2}(\omega-\varphi)}} =\frac{\lambda_1\lambda_2}{\sqrt{\lambda_1^2\sin^2(\omega-\varphi)+\lambda_2^2\cos^2(\omega-\varphi)}}
\end{align}
That is, the singular values form the half-axes of the PCA ellipsoid, which yields us a symbolic definition for our transmission (transfer) function as weighting profiles. We compute the offset angle $\varphi$ w.r.t. x-axis by exploiting the atan2-function with 4-quadrant evaluation for the first singular vector. As a preliminary prep, this profile is precomputed (sampled) for all discrete angular steps for each cell (e.g. $360$). The weighting scheme which we apply is depicted in Fig. \ref{weighting}.
\begin{figure}[h]
  \centering
  {
    \includegraphics[width=0.6\textwidth]
    {img/weighting.png}
  }
  \caption{red: Intensity Profile, cyan: Transmission Profile (Glyph Ellipsoid Eq.)}
  \label{weighting}
\end{figure}
We interpret the polar functions as discrete, sampled 1D vectors with a constant angular resolution. That means, we use element-wise multiplication for the 1D-vectors in red (Intensity Profile) and cyan (Transmission Profile) to obtain a windowed version of the intensity profile and perform the following integration step to accumulate the total radiant power (flux) as follows. Note that we model angular dependent radiant intensity $\mathbf{I}(\omega) [\frac{W}{\mathop{rad}}]$ as an underlying physical entity, which is well suited for describing point light sources:

\begin{align}
	\Phi_t &= \int_0^{2\pi}\mathbf{I}(\omega)\mathbf{T}(\omega)\mathop{d\omega}\\
	\sum_{\cos} &= \int_0^{2\pi}\cos(\omega)\mathop{d\omega} \approx 2
\end{align}

This enables us to scale an oriented cosine-lobe w. the total radiant flux w. respect to its own total energy when integrated likewise. A discrete cosine lobe never reaches its theoretical sum of $2$ exactly in the interval $[0,2\pi]$. Therefore it needs to be computed to account for floating-point precision errors and normalized by following relation (e.g. $\sum_{\cos} = 1.9949204635834517$).
\begin{align}
	\cos_n(\omega) = \frac{\Phi_t}{\sum_{\cos}}cos(\omega)
\end{align}
This yields a cosine lobe, which has an overall energy of $\Phi_t$ if the point light is interpreted with a Lambert-Emitter (cnf. \cite{lindlein}) characteristic (as part or area element of a diffusely reflecting surface).

Now each tensor ellipse equation has a mean transmission rate $[\%]$, which turns out to be a measure or synonym for the total transmitted rate of the total incoming radiant intensity $\int_0^{2\pi}\mathbf{I}(\omega)$. Since energy can not be generated from transmission profiles (only transmitting, not generating), we have to normalize every tensor ellipse equation with the highest mean transmission rate in the field. This restricts the tensor ellipse mean to a maximum of 1.0 for the one with the highest tensor magnitude. We will use the magnitude $\bar{r}_{max}$ from the PCA here for simplicity. Hence the tensor ellipse equations are normalized through the following step:
\begin{align}
	r_n(\omega) = \frac{1}{\bar{r}_{max}}r(\omega)
\end{align}
Notice, that this implements the concept of absorption implicitly, because tensors with a lower mean $\bar{r}$ than $100\%$ lose energy wheras absorption equals $\boldsymbol{\mu} = \mathbf{1}-\mathbf{T}$ here. Now that we have coped with the problem of overall transmission, we are left with another problem that occurs with the weighting functions as that they can yield values above 1. This would potentially generate intensity out of nothing which leads to crucially unstable behaviour. Well, but only in case energy conservation principles were not respected. However, a proper normalization can give corrective remedy. To construct a solution, we ask for the source of the excessive energy. If the tensor mean complies with the constraint $\bar{r}\leq 1.0$, then the energy must lack in some other place (since the overall transmission fulfills the energy conservation constraint in that case). 
\section{Global Illumination Gradient}
\label{sec:ftle}
Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. 
Usw.
